\begin{abstract}
  %% Context and problem
  %By providing computing and storage capabilities closer to data
  %producers and consumers, Edge infrastructures constitute an alternative to Cloud Computing platforms
  %A few systems have been proposed to store and manipulate data in
  %Edge infrastructures. By relying for instance on appropriate
  %replication policies, those systems reduce the impact of the latency
  %as well as the volume of data passing through the network overall.
  %
  Although, there is no major solution to store and manipulate data in
  Edge infrastructures yet, existing proposals demonstrated the relevance of appropriate
  replication strategies to bring contents closer to consumers, reducing the impact of the latency as
  well as the volume of data passing through the network overall.
%
  Unfortunately, locating the closest replica of a specific content requires to
  maintain an up-to-date index of all live replicas along with their
  respective locations.
  %
  %Current proposals built on a centralized service face scalability
  %issues, single point of failure, as well as latency penalities where
  %locating replicas may effectively take more time than actually
  %downloading contents. Instead, data consumer \processes must
  %maintain an up-to-date index themselves. Unfortunately, maintaining
  %an index of all live replicas at every \process would prove overly
  %costly in terms of memory and generated traffic, especially in large
  %scale dynamic systems where \processes create and destroy replicas
  %at any time.
  % 
  Relying on a remote service contradicts with the properties of
  Edge infrastructures as locating replicas may
  effectively take more time than actually downloading contents.
  At the opposite,  maintaining such an index at every \process would prove overly
  costly in terms of memory and generated traffic, especially in an
  edge context where \processes create and destroy replicas at any
  time.
  % while flooding approaches will not enable the maintenance of such
  % an index for each node in large systems,
  
%%% Our proposal
  \noindent In this paper, we introduce \NAME, an efficient and
  decentralized partitioning protocol for dynamic distributed systems:
  When a \node hosts a replica, it notifies all and only \nodes (new
  members of its partition) that are closer from it than any other
  replica; When a \node destroys a replica, it notifies members of its
  partition to switch to another closer partition. \NAME guarantees
  that eventually, every \process knows its best partition, hence its
  closest replica, despite concurrent operations and receipt orders.
  Our complexity analysis supported by simulations shows that \NAME
  scales well in terms of generated traffic and convergence time, for
  the effect of operations remains lock down to its logical
  partition. While \NAME tackles our content indexing problem, it can
  be used as a building block to design new advanced services such as
  decentralized recommendation systems.
\end{abstract}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../paper"
%%% ispell-local-dictionary: "english"
%%% End: 
