We thank the reviewers for their thorough reading and interesting
comments.  We understand that althought the paper is relevant, some
parts should be clarified. We would be happy to be shepperded if
reviewers believe it is relevant.

Below, we reply to each remark in more detail.

- R1.1. "forwarding the best known partition" consists in transmitting
the best location where to get the replica.  It could be more formally
defined.

- R1.2.  We agree ``Theorem'' is more appropriate than
``Corollary''. Regarding the proof, additional information would be
given (under shepperding).

- R1.3. Regarding Theorem 2, we chose to list all cases to help
understand the algorithm.  Every Add/Del operation creates a small
subset of events that depends on its nature, and the neighbors'
history. This allows us to perform a neighbor-to-neighbor analysis of
cases and avoid any combinatorial explosion.

- R2.1. Our objective is to introduce AS-cast and its properties in a
generic manner.  Hence, experiments focus on evaluating the
correctness/costs of our protocol.  As stated in Conclusion, we plan
to assess the use of AS-cast in IPFS distributed storage. This study
would clarify its tradeoff depending on object size, update frequency,
etc.

- R2.2. AS-cast is more efficient than CDN: it allows (i) retrieving
the closest location eventually and (ii) partitioning the
infrastructure dynamically according to the creation/removal of
replicas. Contrarily, CDN relies on a static partitioning of the
infrastructure: nodes get replicas from a subset of specific nodes and
for all objects. A node may contact a peer of the CDN infrastructure
while a replica may exist only one hop away (replicated by one of its
neighbors).  AS-cast natively deals with such cases as any node can
serve a replica.

- R2.3.  The scalability issue related to the management of thousands
of objects should be addressed. As stated in Conclusion, we propose to
leverage the hierarchical properties of inter-autonomous systems to
avoid flooding uninterested nodes.  However, this increases the
complexity to prove that our protocol still converge.

- R3.1. In addition to R2.3, we confirm that partitioning is
per-object.  Yet, it would be straightforward indeed to mutualize
traffic, e.g., using dedicated propagation windows to consolidate
control messages together.

- R3.2. AS-cast does not handle replication strategies. If it exists
only one source and it crashes, this reference eventually disappears
from the system. AS-cast reacts similarly to crashes and departures of
sources (see Algorithm 3 Line 4) to update the best partition known by
impacted nodes.

- R3.3. We do not address the issue of content mutability.  From our
viewpoint, this aspect is application-dependent. For instance,
mutability could be provided by versioning as done in IPFS, BlobSeer,
etc.

- R3.4. Regarding the experiments remarks, please, refer to R2.2.

- R3.5. Several approaches tackle the indexation problem in NDN. We
were unaware of NDNS and agree to add it in Related Work.

- R3.6. Although network topologies include triangular inequalities,
they do not endanger the AS-CAST correctness (AS-CAST relies on the
shortest distance between vertices).

